---
title: "Data Products Course Week 4 Project -function plot"
author: "Ehsan Pourhadi"
date: "August 28, 2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
This presentation deals with plot a polynomial function as project for Data Products Course in week 4.

The application demo built by Shiny and can be observed at the URL: https://epourhadi.shinyapps.io/Shiny-Application-and-Reproducible-Pitch/

Source codes incluiding **ui.R** and **server.R** are at GitHub for the application and presnetation at the URL:

https://github.com/epourhadi/shiny-application-and-reproducible-pitch

## Goal of our Web Application 

This web application is built to study the geometric shape of a third order polynomial 
in 2-dimensional space by changing the three coefficients. 

## For user only

Our application provides user with some different inputs:

- The defined function "calculateParabola" is the important part of the body of web application and three variables (subjected to this study) are defined here.

- Consider the lower and upper bounds "xlim" and "ylim" in Cartesian coordinates.

- Consider the commands "geom_line" and "geom_vline" (for vertical lines), "geom_hline" (for horizontal lines) and "geom_point".


## Look at plot for some fixed parameters 
For the coefficients 1,0,0 as initial values of our variables we get:
```{r}
y<-function(x) (1 * (0 - x)^3 +0*x)
plot(y, xlim=c(-10,10))
```



